Kyoto VR MQP Paper First Draft

### 2019-09-23 paper.tex
wrapping up section on editour

The user can easily create a new region by shift-clicking, and then clicking
points on the map. To terminate the polygon, the user must shift-click again.
A user can only terminate the polygon after two points have been placed to
prevent the user from drawing a region with an area of zero. Once a region is
created, a region card appears in the side bar. From here, the user can edit
anything about the region. From here, the user can edit anything about the
region.

@@

>>>>

The user can easily create a new region by shift-clicking, and then clicking
points on the map.  To terminate the polygon, the user must shift-click again.
The ``Welcome to editour'' card provides these instructions, which should be
enough to get started.  A user can only terminate the polygon after two points
have been placed to prevent the user from drawing a region with an area of
zero. Once a region is created, a region card appears in the side bar. From
here, the user can edit anything about the region. From here, the user can edit
anything about the region.

@@

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins/libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button. We also hard-coded some shortcuts for places that Atticus
might want to design a tour for in the future, which can be accessed by
clicking on the yellow buttons with place names.

Once a tour is either uploaded or downloaded, a link to download the zip file
will appear. The zip file contains all of the uploaded media, and a metadata
file. The metadata is in the form of a JSON file; it contains all of the
latitudes, longitudes, and enough information to associate all of the media
with the correct regions. This is the file that we unzip and place into the
Unity project before it is compiled. This also is useful if the user wants to
check the audio and image files that were uploaded.
